The paper on \Large \bf Blockchain Frontrunning

### 2018-09-13 frontrunning/Latex/sections/paper.tex
[frontrunning] Revisions on Preliminaries

The concept of the \emph{front-running} goes back to decades ago when financial instrument markets first started. Initially the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change. Clearly in such scenarios front-running was possible yet not detectable as a damaging activity. However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore and new form of front-running is feasible through high speed networks. Furthermore, Blockchain technology has introduced transparency and open markets and leads to a new era of front-running which inherently affects all decentral applications, whether financial or non-financial. Arbitrage and Censorship, are also issues that have been linked to front-running attacks on blockchain \textit{(We need to talk about why these two are left out of the scope of this paper)}. Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a s specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} Using this criteria, we successfully categorized these decentral application s into 5 principal categories on which we conduct our analysis. Surprisingly, there was no ICO (initial coin offering) included in the top 25 Dapps list by the time we fetched the data from the website. We believe the reason is because the ICOs are inherently different from other groups of Dapss as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over. Therefore, we  consider ICOs as another cases on which the front-running should be investigated (although they are not listed in the top 25 Dapps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}

@@

\subsection{Traditional Front-running} %Definition of front-running
\label{sec:What is front-running?}

\emph{Front-running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information about upcoming transactions and trades. This problem can occur in both financial and non-financial systems, however, it is more noticeable within the trading and exchange systems as it was originated back in stock markets. In the old times, all the trades were executed on papers, so in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed. Therefore, a malicious trader would now run in front of that order and put his own transaction in-between (before the trade was executed) and profit from the price increase of the stock. In other words, a group of market participants obtain non-public market information which allows them to front-run other user\'s trades by putting their orders ahead of those trades and benefit from advance knowledge of pending client orders. The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}. Any sort of front-running activity within the financial markets is considered as an unethical and illegal practice as it is unfairly beneficial for a few market participants who have the privilege of acting on this information and taking advantages at the expense of the investors.

%\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
As traditional front-running has been the subject of discussion for decades, there are many literatures on this subject. Here we focus on the historical context and how the regulations evolved to be what they are today.\\
Front-running was first appeared on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by \textit{Securities Exchange Commission} in 1977 as the following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978optionsmarket}
\end{quote}

@@

\subsection{How are Blockchain Applications Vulnerable to Front-running?} 
\label{sec:Front Running on the Blockchains}

Blockchain technology has received an exceptional amount of attention since it was first introduced as the underlying technology of the cryptocurrency Bitcoin in 2008~\cite{nakamoto2008bitcoin}. Many decentralized applications that are built on top of this technology represent the significance of the blockchain as it completely eliminates the central point of failure within any systems. However, blockchains have some inherent characteristic that leave them vulnerable to \emph{front-running} behavior. Although this data structure is known to be publicly visible to every network participants, information is layered  and some of them are accessed only by insiders. Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in Section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front-running. Decentralized exchanges are a group of blockchain financial applications where front-running can be executed. 
Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from potential price increase of the market stocks (details are provided in~\ref{sec:frontrunningExchanges}). Decentralized namespaces, as blockchain non-financial applications, are another example. Ethereum Name Service and Ghazal \cite{moosavighazal} are such systems in which upon seeing a transaction from Alice to register \texttt{alice.eth}, front-runner can go ahead of her and register this domain name. He can later sell \texttt{alice.eth} to Alice for a higher price and profit.
Another application that is vulnerable to front-running is Initial Coin Offering (ICO) smart contracts. ICO is a method to distribute tokens based on the deposits of the native coin, Ether in the case of Ethereum. After a few hacking incidents on high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to late comers on the open markets~\cite{zetzsche2018ico, li2018initial}. ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.  This competition made ICOs a good opportunity for front-running attacks.  In this paper we use multiple empirical examples to show possibility of front-running on DApps, for the sake of completeness, we use one incident on ICOs, and examples from the Top 25 DApps by recent user counts. %TODO: this last sentece is a bit weird here!

\subsection{Literature on Blockchain Front-running}
There are only a few research carried out on the front-running subject in the context of blockchain and decentral ledgers. \\

Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}. As mentioned in Section~\ref{sec:What is front-running?}, the information leakage results the entire system to be vulnerable to the front-running. They also propose a cryptographic approach, similar to commit and reveal(~ref{CommitmentScheme}), to prevent front-running in decentral systems. %In this approach, which is similar to commit and reveal , a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information. Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast. This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.
Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers ~\cite{malinova2017market}.  They argue that blockchain brings a new options of transparency which affects traders behavior, specially in the presence of intermediary front-runners. They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient.

@@

%
%___________________________________________________________%
%\section{Related Work}
%As the traditional front-running was originated in trading financial instruments most of the literature are focused on financial aspects of the markets.  However, there are also a few policies regarding domain name registration front-running~\cite{sac022en33:online}

>>>>

The concept of the \emph{front-running} goes back to decades ago when financial instrument markets first started. Initially the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change. Clearly in such scenarios front-running was possible yet not detectable as a damaging activity. However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore and new form of front-running is feasible through high speed networks. Furthermore, Blockchain technology has introduced transparency and open markets and leads to a new era of front-running which inherently affects all decentral applications, whether financial or non-financial. Arbitrage and Censorship, are also issues that have been linked to front-running attacks on blockchain \textit{(We need to talk about why these two are left out of the scope of this paper)}. Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a s specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} Using this criteria, we successfully categorized these decentral application s into 5 principal categories on which we conduct our analysis. Surprisingly, there was no ICO (initial coin offering) included in the top 25 Dapps list by the time we fetched the data from the website. We believe the reason is because the ICOs are inherently different from other groups of Daaps as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over. Therefore, we  consider ICOs as another cases on which the front-running should be investigated (although they are not listed in the top 25 Dapps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}

@@

\subsection{Traditional Front-running} 
\label{sec:What is front-running?}

\emph{Front-running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information about upcoming transactions and trades. This problem can occur in both financial and non-financial systems, however, it is more noticeable within the trading and exchange systems as was originated back in the stock markets. In the old times, all the trades were executed on papers, so in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed. Therefore, a malicious trader would run in front of that order and put his own transaction in-between (before the trade was executed) and hence profit from the price increase of the stock. In fact, a group of market participants obtain non-public market information which allows them to front-run other user\'s trades by putting their orders ahead of those trades and benefit from advance knowledge of pending client orders. The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}. Any sort of front-running activity within the financial markets is considered as an unethical and illegal practice as it is unfairly beneficial for a few market participants who have the privilege of acting on this information and taking advantages at the expense of the investors.

\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
As traditional front-running has been the subject of discussion for decades, there are many literatures on this subject. Here we focus on the historical context and how the regulations evolved to be what they are today.\\
Front-running was first appeared on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by \textit{Securities Exchange Commission} in 1977 as the following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978optionsmarket}
\end{quote}

@@

\subsection{Blockchain Front-running} % for the unity of the paper, the previous title : How are Blockchain Applications Vulnerable to Front-running? is changed to "Blokcchain front-running", in this case the other section's name (on blockchain frontrunning, where we talk about miner and non miner frontrunning) needs to change to sth different and more descriptive.
\label{sec:Front Running on the Blockchains}

Blockchain technology has received an exceptional amount of attention since it was first introduced as the underlying technology of the cryptocurrency Bitcoin in 2008~\cite{nakamoto2008bitcoin}. Many decentralized applications that are built on top of this technology represent the significance of the blockchain as it completely eliminates the central point of failure within any systems. However, blockchains have some inherent characteristic that leave them vulnerable to \emph{front-running} behaviour. Although this data structure is known to be publicly visible to every network participants, information is layered and some of them are accessed only by insiders. Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in Section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front-running. Decentralized exchanges are a group of blockchain financial applications where front-running can be executed. 
%____________________________________________________________________
%%% The following chunk seem to be redundant and weird. Should we keep it?? 
Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from potential price increase of the market stocks (details are provided in~\ref{sec:frontrunningExchanges}). Decentralized namespaces, as blockchain non-financial applications, are another example. Ethereum Name Service and Ghazal \cite{moosavighazal} are such systems in which upon seeing a transaction from Alice to register \texttt{alice.eth}, front-runner can go ahead of her and register this domain name. He can later sell \texttt{alice.eth} to Alice for a higher price and profit.
Another application that is vulnerable to front-running is Initial Coin Offering (ICO) smart contracts. ICO is a method to distribute tokens based on the deposits of the native coin, Ether in the case of Ethereum. After a few hacking incidents on high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to late comers on the open markets~\cite{zetzsche2018ico, li2018initial}. ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.  This competition made ICOs a good opportunity for front-running attacks.  In this paper we use multiple empirical examples to show possibility of front-running on DApps, for the sake of completeness, we use one incident on ICOs, and examples from the Top 25 DApps by recent user counts. %TODO: this last sentece is a bit weird here! 
%____________________________________________________________________

\subsection{Literature on Blockchain Front-running}

Due to the novelty characteristics of the underlying technology (blockchains) and the issue of front-running, there are only a few research carried out on this subject in the context of blockchain and decentral ledgers. \\
Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}. As mentioned in Section~\ref{sec:What is front-running?}, the information leakage results the entire system to be vulnerable to the front-running. They also propose a cryptographic approach, similar to commit and reveal(~ref{CommitmentScheme}), to prevent front-running in decentral systems. %In this approach, which is similar to commit and reveal , a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information. Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast. This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.
Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers ~\cite{malinova2017market}.  They argue that blockchain brings a new options of transparency which affects traders behavior, specially in the presence of intermediary front-runners. They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient.

@@

%___________________________________________________________%
